The Power of Unbiased Recursive Partitioning:\\ A Unifying View of CTree, MOB, and GUIDE

### 2019-02-13 pkg/partykit/inst/guideliketest/draft/draft.Rnw
revision on discussion; correct paths in simulation code
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2463 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: d1f8ff4b6250a557ba335c0c39dc0d75c0087fc8

>>>>

Note that considering full model scores is particularly advantageous if the model parameters do not
depend on each other, hence are orthogonal, as it is the case for the intercept and slope parameter
of a linear model. On the other hand, if all parameters are closely correlated with the location parameter
a residual-based approach might be able to detect changes in other parameters than the mean as well,
however, the performance of a score-based search for split variables is not negatively effected.
